### 2010-06-14 subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: filemonitor, new converters: html, htmlhead

The files that the monitor can process are images, SVG files and files created
for GraphWiz.

@@

>>>>

The files that the monitor can process are images, SVG files, dot files created
for GraphWiz, LuaGl scripts, HTML chunks.

@@

The converters {\em luagl}, {\em html} and {\em htmlhead} send the unprocessed
contents of the monitored file to the server.
